Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-21 final_metrics_analysis.Rmd
Adding description of recidivism mosaic chart

```{python exploratory recidivism mosaic plot}
props={}
props[('Caucasian','Recidivated')]={'facecolor':'red', 'edgecolor':'white'}
props[('Caucasian','Survived')]={'facecolor':'red', 'edgecolor':'white'}
props[('African-American','Recidivated')]={'facecolor':'xkcd:aqua','edgecolor':'white'}
props[('African-American','Survived')]=        {'facecolor':'xkcd:aqua','edgecolor':'white'}
labelizer=lambda k:{('Caucasian','Recidivated'):1278,('African-American','Recidivated'):1661,('Caucasian','Survived'):1278,('African-American','Survived'):1512}[k]
mosaic(df_viz,['race','two_year_recid'],labelizer=labelizer,properties=props)
plt.show()
```

>>>>

```{python exploratory recidivism mosaic plot}
props={}
props[('Caucasian','Recidivated')]={'facecolor':'red', 'edgecolor':'white'}
props[('Caucasian','Survived')]={'facecolor':'red', 'edgecolor':'white'}
props[('African-American','Recidivated')]={'facecolor':'xkcd:aqua','edgecolor':'white'}
props[('African-American','Survived')]=        {'facecolor':'xkcd:aqua','edgecolor':'white'}
labelizer=lambda k:{('Caucasian','Recidivated'):822,('African-American','Recidivated'):1661,('Caucasian','Survived'):1278,('African-American','Survived'):1512}[k]
mosaic(df_viz,['race','two_year_recid'],labelizer=labelizer,properties=props)
plt.show()
```

A higher percentage of white defendants (60.86%) than black defendants (47.65%) did not commit another crime within two years. This means that 39.14% of white defendants did recidivate within two years compared to 52.35% of black defendants.
